%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS (DO NOT CHANGE)
%----------------------------------------------------------------------------------------

\documentclass[margin, 11pt]{res} % Use the res.cls style, do not change font size at 11pt

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{eurosym}


\linespread{1.0}
\usepackage[T1]{fontenc}

\usepackage{fancyhdr}
\pagestyle{plain}
\cfoot{\thepage}


\usepackage{color}
\usepackage[colorlinks=true,
            linkcolor=red,
            urlcolor=blue,
            citecolor=gray]{hyperref}

% Change margins and width (DO NOT CHANGE)

\setlength{\textwidth}{5.8in} % Text width of the document
\setlength{\textheight}{8 in} % increase text height to fit on 1-page 
\addtolength{\oddsidemargin}{-.3in}
\addtolength{\evensidemargin}{-.875in}
%	\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-.3in}
\addtolength{\textheight}{1.5in}

\hangindent=1em

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------


\name{\bf{\huge{Cristiano Cantore}}\\[14pt]}  


\vspace{5cm}

\address{Sapienza Universit\`{a} di Roma\\Dipartimento di Economia e Diritto\\
Via del Castro Laurenziano, 9\\ 6sto Piano Ala B\\ 00161 Roma}

\address{ E-mail:  \href{mailto:cristiano.cantore@uniroma1.it}{\nolinkurl{cristiano.cantore@uniroma1.it}} \\  
Web: \url{http://www.cristianocantore.com} %\\Phone: +44 (0)2034614469
}   



%----------------------------------------------------------------------------------------

\begin{resume}

\section{\sc{Fields of\\ Interest}}
Business Cycle Theory, Monetary and Fiscal Policy, Applied Macroeconomics\\


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{\sc{Current Employment}}
\textbf{Professor of Economics}, Sapienza University of Rome. \hfill  from 03/2023\\


\section{\sc{Other Affiliations}}
Fellow at the Centre for Macroeconomics (LSE), the Rimini Centre for Economic Analysis and Centre for International Macroeconomics (Surrey). \\

\section{\sc{Education}}
\textbf{Ph.D. in Economics} University of Kent,  (passed without corrections). \hfill 2011 \\
\hspace*{5mm}Dissertation Examiners:  Prof. M. Ellison (Oxford), Dr. K.Shibayama (Kent).\\
% or use the following line
%\hspace*{5mm}Main Advisor:  First Advisor
\textbf{M.Sc. in Economics}, Pompeu Fabra University, Barcelona.    \hfill 2005\\
\textbf{B.A. in Economics and Statistics},  L. Bocconi University, Milan.   \hfill 2004

\section{\sc{Previous Positions}}
\textbf{Guest Lecturer}, London School of Economics, London. \hfill 01/2022 to 07/2022\\
\textbf{Bank of England Pole Director} at the Centre for Macroeconomics (LSE).  \hfill  02/2021 to 02/2023\\
\textbf{Research Advisor}, Research Hub, Bank of England. \hfill  07/2021 to 02/2023\\
\textbf{Reader in Economics} (Part-Time), University of Surrey, Guildford. \hfill 08/2018 to 02/2023\\
\textbf{Senior Research Economist}, Research Hub, Bank of England. \hfill  09/2018 to 06/2021\\
\textbf{Senior Lecturer in Economics}, University of Surrey, Guildford. \hfill 04/2013 to 07/2018\\
\textbf{Visiting Professor}, Collegio Carlo Alberto, Turin. \hfill 10/2021 to 10/2021\\
\textbf{Visiting Professor}, University of California San Diego. \hfill 02/2014 to 07/2014\\
\textbf{Visiting Research Fellow}, Banco de Espa\~{n}a, Madrid. \hfill 04/2012 to 08/2012\\
\textbf{Lecturer in Economics}, University of Surrey, Guildford. \hfill 09/2009 to 03/2013\\
\textbf{Visiting Professor}, University of Cagliari. \hfill 01/2012 to 02/2012\\
\textbf{Intern}, European Central Bank, Economics DG. \hfill 08/2008 to 10/2008\\
\textbf{Intern}, OECD, Economic Department, Country desk 1. \hfill 07/2007 to 09/2007


%----------------------------------------------------------------------------------------
%	RESEARCH
%----------------------------------------------------------------------------------------




\section{\sc{Publications}}
(2025) \emph{\href{https://www.sciencedirect.com/science/article/pii/S0014292125000297}{Monetary–fiscal interaction and the liquidity of government debt}}, joint with Edoardo Leonardi (London School of Economics).
\textbf{European Economic Review}, 173, 104979.\\
\\
(2024) \emph{\href{https://www.sciencedirect.com/science/article/pii/S0014292124001946?dgcid=author}{Unwinding quantitative easing: State dependency and household heterogeneity}}, joint with Pascal Meichtry (Banque de France).
\textbf{European Economic Review}, 170, 104865.\\
\\
(2021) \emph{\href{https://www.sciencedirect.com/science/article/abs/pii/S0304393221000040}{Workers, Capitalists, and the Government: Fiscal Policy and Income (Re)Distribution}}, joint with Lukas Freund (University of Cambridge).
\textbf{Journal of Monetary Economics}, 119, 58-74.\\
\\
(2020) \emph{\href{https://academic.oup.com/jeea/advance-article/doi/10.1093/jeea/jvaa034/5884931}{The Missing Link: Labor Share and Monetary Policy}}, joint with Filippo Ferroni (Chicago FED) and Miguel Le\'{o}n-Ledesma (University of Kent).
\textbf{Journal of the European Economic Association}, 19(3), 1592–1620.\\
\\
(2019) \emph{\href{https://www.cambridge.org/core/journals/macroeconomic-dynamics/article/optimal-fiscal-and-monetary-policy-debt-crisis-and-management/4E05CEF51FA691092B6EE52ACC807F5E}{Optimal Fiscal and Monetary Policy, Debt Crisis and
Management}}, joint with  Paul Levine (University of Surrey), Giovanni Melina (IMF) and Joseph Pearlman (City University London). \textbf{Macroeconomic Dynamics}, 23-3, 1166-1204.\\
\\
(2017) \emph{\href{http://www.sciencedirect.com/science/article/pii/S016518891730115X}{The Dynamics of hours worked and technology}}, joint with Filippo Ferroni (Chicago FED) and Miguel Le\'{o}n-Ledesma (University of Kent).
\textbf{Journal of Economic Dynamics and Control}, 82, 67-82.\\
\\
(2015) \emph{\href{https://www.sciencedirect.com/science/article/pii/S0165188915001736}{CES technology and Business Cycle fluctuations}}, joint with Paul Levine (University of Surrey), Joseph Pearlman (City University London) and Bo Yang (Swansea University).
\textbf{Journal of Economic Dynamics and Control}, 61(C), 133-151.\\
\\
(2014) \emph{\href{http://onlinelibrary.wiley.com/doi/10.1111/jeea.12038/abstract}{Shocking Stuff: Technology, Hours and Factor Substitution}}, joint with Miguel Le\'{o}n-Ledesma (University of Kent), Peter McAdam (ECB) and Alpo Willman (ECB). 
\textbf{Journal of the European Economic Association}, 12-1, 108-128\\
\\
(2014) \emph{\href{http://onlinelibrary.wiley.com/doi/10.1111/sjoe.12066/abstract}{A Fiscal Stimulus and Jobless Recovery}}, joint with  Paul Levine (University of Surrey) and Giovanni Melina (IMF). \textbf{Scandinavian Journal of Economics}, 116-3, 669-701\\
\\
(2012) \emph{\href{http://www.sciencedirect.com/science/article/pii/S0165188912001339}{Getting Normalization Right: Dealing with 'Dimensional Constants' in Macroeconomics}}, joint with Paul Levine (University of Surrey). \textbf{Journal of Economic Dynamics and Control},  36, 1931-1949\\
\\
(2012) \emph{\href{http://www.sciencedirect.com/science/article/pii/S0165176512003199}{A Fiscal Stimulus with Deep Habits and Optimal Monetary Policy}}, joint with  Paul Levine (University of Surrey), Giovanni Melina (IMF) and Bo Yang (Swansea University). \textbf{Economics Letters}, 117-1, 348-353

\subsection{\sc{Book Chapters}}
(2013)\emph{The Science and  Art of DSGE Modelling I. Construction and Bayesian Estimation}, joint with V. Gabriel,  P. Levine, J. Pearlman and B. Yang.   in  '\textbf{Handbook of Research Methods and Applications in Empirical Macroeconomics}', eds N. Hashimzade and M. Thornton,  Edward Elgar Publishing\\
\\
(2013)\emph{The Science and  Art of DSGE Modelling  II.~Model Comparisons, Model Validation, Policy Analysis and General Discussion}, joint with V. Gabriel,  P. Levine, J. Pearlman and B. Yang. in  '\textbf{Handbook of Research Methods and Applications in Empirical Macroeconomics}', eds N. Hashimzade and M. Thornton,  Edward Elgar Publishing


%\section{\sc{Working\\ Papers} }
%\\





%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------


\section{\sc{Relevant Experience}}

\textbf{Teaching}

\begin{itemize}
    \item \textbf{Sapienza University of Roma - (2023 to date)}:
    \begin{itemize}
        \item \emph{Undergraduate}: Politica Economica. 
        \item \emph{Masters}: Economic Policy, Teorie e Politiche Macroeconomiche.  
    \end{itemize}

    \item Monetary Economics and Aggregate Fluctuations, \emph{Master in Economics} \textbf{London School of Economics}, London. \hfill Jan-Apr. 2022 
    \item Introduction to Dynamic Macroeconomics, \emph{Master in Economics}, \textbf{Collegio Carlo Alberto}, Turin. \hfill 5-15/10/2021 
    \item \textbf{University of Surrey - (2009 to 2022)}:

\begin{itemize}
	\item \emph{Undergraduate}: Intermediate Macroeconomics Theory and Applications; International Economics and Finance; Economic Data Analysis. 
	\item \emph{Masters}: Macroeconomics; International Trade; Advanced Economic Theory. 
	\item \emph{PhD}: Advanced Macroeconomics I; Topics in Empirical Macroeconomics. 
\end{itemize}
\end{itemize}


 % \newpage % Delete depending on your length of CV

\textbf{Training courses on DSGE models}

%\begin{itemize}
Central Bank of Paraguay, Assunción. \hfill 24-26/02/2025 \\
CIMS Winter School, University of Surrey. \hfill 09/12/2024 \\
CIMS Summer School, University of Surrey. \hfill 10/09/2024 \\
Central Bank of Paraguay, Online. \hfill 15-26/03 \& 3-4/04/2024 \\
CIMS Summer School, University of Surrey. \hfill 11-15/09/2023 \\
CIMS Summer School, University of Surrey. \hfill 12-16/09/2022 \\
CIMS Summer School, University of Surrey. \hfill 7-14/09/2021 \\
CIMS Summer School, University of Surrey. \hfill 7-11/09/2020 \\
CIMS Summer School, University of Surrey. \hfill 9-13/09/2019 \\
CIMS Summer School, University of Surrey. \hfill 3-7/09/2018 \\
CIMS Summer School, University of Surrey. \hfill 4-8/09/2017\\
DIW, Berlin. \hfill 25-26/07/2017 \\
CIMS Summer School, University of Surrey. \hfill 30/8-3/9/2016\\
Central Bank of Nigeria, Abuja. \hfill 6-10/06/2016 \\
Central Bank of Nigeria, Abuja. \hfill 25-29/01/2016\\
CIMS Summer School, University of Surrey. \hfill 7-11/09/2015\\
Computational Economics Summer School, University of Cagliari. \hfill 6-9/07/2015\\
CIMS Easter School, University of Surrey. \hfill 20-22 April 2015\\
CIMS Summer School, University of Surrey. \hfill 8-13/09/2014\\
CIMS Summer School, University of Surrey. \hfill 9-13/09/2013\\
RES Easter School, University of Birmingham. \hfill 14-18/04/2013\\
CIMS Summer School, University of Surrey. \hfill 10-14/09/2012 \\
PhD program, University of Porto, Portugal. \hfill 30/1-2/2/2012\\
Scottish PhD program, University of Glasgow, Scotland. \hfill 5-6/7/2011\\
National Institute of Public Policy and Finance, New Delhi, India. \hfill 31/1-4/2/2011

%\end{itemize}	

\textbf{Administration Duties}

Member of the Senate, University of Surrey. \hfill 2017-2018\\
Job market committee (committee chair in 2015), University of Surrey. \hfill 2012-2018\\
Deputy Head of School, University of Surrey. \hfill 2015\\
 PhD admission director, University of Surrey. \hfill 2014-2018\\
Undergraduate admission officer; Departmental seminars organizer. University of Surrey. \hfill 2009-2013

%----------------------------------------------------------------------------------------
%	OTHER
%----------------------------------------------------------------------------------------
\section{\sc{Consulting and Research Projects}}
\begin{itemize}
\item "Impact of monetary policy on households' desired labour supply in the euro area", DG-ECFIN European Commission Tender \hfill 06/2024-09/2025.
\item "Methodology and measurement update of the Gender Equality Index", FWC EIGE/2023/OPER/05 - Lot 2. Consulting for Fondazione Brodolini \hfill 12/2024-01/2026.
\end{itemize}

\section{\sc{Grants, \\ Awards \\  Editorial activities and Committees}}
\begin{itemize}
\item Organized 4th Sailing the Macro Workshop, Ortygia. \hfill 2024.
\item Organized Workshop on Household Heterogeneity, Inflation, and the Green Transition, Sapienza University. \hfill 2024.
\item ESRC Peer Review College member. \hfill 2023 to date 
\item Organized 3rd Sailing the Macro Workshop, Ortygia. \hfill 2023.
\item Scientific committee of the MMF annual conference. \hfill 2023 to date.
\item Money, Macro and Finance Society committee member. \hfill 2023 to 2024 
\item Editor of the Bank of England Staff Working Papers. \hfill 2018 to 2023
\item Organized \emph{\href{https://www.mmf.ac.uk/phd/2022-phd-conference/}{9th Annual MMF PhD Conference}}. \hfill 21/23-04-2022
\item Organized \emph{\href{https://www.bankofengland.co.uk/events/2022/february/first-annual-bear-conference}{First Annual BEAR Conference: The Monetary Toolkit}}. \hfill 25/26-02-2022
\item Organized workshop on \emph{\href{https://www.mmf.ac.uk/productivity-workshop/}{Productivity and Structural Change}} sponsored by NIESR, The productivity institute, MMF and the Bank of England. \hfill 26-11-2021
\item Organized the  \emph{\href{https://www.bankofengland.co.uk/events/2021/may/mmf-workshop-on-macroeconomic-consequences-of-technological-change}{Macroeconomic Consequences of Technological Change workshop}} sponsored by MMF, University of Kent and the Bank of England. \hfill 10/11-6-2021
\item Organized conference \emph{\href{https://www.dropbox.com/s/vfv3qz5ixi32ywf/Programme.pdf?dl=0}{Income Distribution, Wealth Distribution and Central Bank Policies}} sponsored by CFM, LSE and the Bank of England. \hfill 28-2-2020
\item Scientific committee \emph{Money, Macroeconomics and Finance PhD conference}. \hfill 2018
\item European Commission / Type of funding scheme: CO-CREATION-08-2016/2017: Modelling and evaluating the socio-economic impacts of research and innovation with the suite of macro- and regional-economic models. 323,440\euro$\,$  at fEC  as co-investigator. \hfill 2017-2018
\item Scientific committee \emph{Spanish Economic Association Simposio}. \hfill 2013-2015
\item RES Special Project Grant funding the \emph{2nd Workshop on Structural Change \& Macroeconomic Dynamics.} 2,600\textsterling \hfill 2012
\item Banco de Espa\~{n}a Fellowship 'Trabajos de investigaci\'{o}n sobre econom\'{i}a'. \hfill 2012
\item ESRC grant: Monetary and Fiscal Policy Rules with Labour Market and Financial Frictions. 347,000\textsterling$\,$  at fEC  as co-investigator. \hfill 2010-2012 
\item ESRC PhD scholarship, University of Kent. \hfill 2006-2009
\item Postgraduate scholarship, Carlos III University. \hfill 2005-2006
\end{itemize}


\section{\sc{Conferences and Presentations}}
\textbf{2025:} {BSE Summer Forum, Barcelona;University of Bonn; Banco Central de Paraguay, Assunción.}
\\
\textbf{2024:} {2024 Quantitative Macroeconomics Workshop, Reserve Bank of Australia, Sydney; Banco Central de Colombia, (Online); 3rd Dynare Workshop for Advanced Users, JRC Ispra; ICMAIF 2024, University of Crete; Padova Macro Talks 2024, University of Padua; Paris School of Economics; EIEF (Rome); European Commission, DG ECFIN (Online); Society of Nonlinear Dynamics and Econometrics, University of Padova.}
\\
\textbf{2023:} {ASSA Meetings 2023, New Orleans; University of York; Bank of England; Norges Bank; FinPro3, Bank of Italy; EEA-ESEM23, Universitat Pompeu Fabra, Workshop on Macroeconomics and Survey Data, National Bank of Belgium.}
\\
\textbf{2022:} {Theories and Methods in Macroeconomics 2022, Kings College London; Royal Economic Society (invited for policy discussion), University of Reading; Banca d'Italia; Society for Nonlinear Dynamics and Econometrics 2022, Online; Universitat Autonoma de Barcelona; Barcelona Summer Forum: Monetary Policy and Central Banking, Universitat Autonoma de Barcelona; Salento Macro Meetings, Lecce; Universit\`{a} La Sapienza, Roma; Universit\'{e} catholique de Louvain; Household Heterogeneity conference, Banque de France; 4th European Midwest Micro/Macro Conference (EM3C), Frankfurt School of Finance and Management.}
\\
\textbf{2021:} {11th ifo Conference on Macroeconomics and Survey Data, Ifo Institute; University of Surrey; CFM workshop, LSE; 3TM, Banque de France; 8th Bank of Italy-CEPR Conference on Money, Banking and Finance: “Closing the Gaps: The Future of Stabilisation Policies after the COVID-19 Pandemic”, Bank of Italy; EEA/ESEM 2021; 52nd MMF Annual conference; 1st Sailing the Macro Workshop, Ventotene; Collegio Carlo Alberto, Turin; Macroeconometric Workshop, King's College London; Universidad de Antioquia, Medell\'{i}n; Workshop on Empirical Monetary Economics 2021, SciencePo, Paris; European Winter Meeting of the Econometric Society 2021, UB, Barcelona.}
\\
\textbf{2020:} {Birkbeck, University of London; EEA/ESEM 2020, University of Rotterdam; 2020 Central Bank Macro Modelling Workshop, Norges Bank; XXV meeting of the Central Bank Researchers Network (CEMLA), Banco Central del Uruguay.}
\\
\textbf{2019:} {Banca d'Italia; 7th Belgian Macroeonomic Wokshop (\textbf{invited lecture}), University of Ghent; EEA/ESEM 2019, University of Manchester; 3rd Workshop on 'Macroeconomic and Financial Time Series Analysis', University of Lancaster; CEPR Network on Macroeconomic Modelling and Model Comparison, Goethe University Frankfurt; 2019 Royal Economic Society Annual Conference, University of Warwick; International Monetary Fund, Washington DC; 27th Annual Symposium of the Society for Nonlinear Dynamics and Econometrics, Dallas FED. 'Labor Income Share Developments: Drivers and Policy Implications', Bank of Greece, Athens.}
\\
\textbf{2018:} {Ridge Forum December 2018: Macroeconomics and Development, Buenos Aires; 6th Workshop in Macro Banking and Finance, Alghero; 71st European Meeting of the Econometric Society, Cologne; Bank of England; 14th Dynare Conference, European Central Bank; Deutsche Bundesbank, Frankfurt; Universitat de Barcelona; Universit\'{e} de Lorraine, Nancy.} 
\\
\textbf{2017:} {16th workshop "Macronomic Dynamics: theory and applications", Universit\`{a} Cattolica de Sacro Cuore Milano;  XI Workshop on Public Design: "Structural Changes, Labor Markets and Policy", Universitat de Girona; Bank of Japan, Tokyo; 13th Dynare Conference, Univeristy of Tokyo; Universit\`{a} di Verona; DIW, Berlin; 1st Research Conference of the CEPR Network on Macroeconomic Modelling and Model Comparison MMCN, Goethe University Frankfurt; Bank of England, London; International Monetary Fund, Washington DC; Federal Reserve Bank, Chicago; Collegio Carlo Alberto, Turin; University of Surrey; University of Kent.} 
\\
\textbf{2016:} {University of Portsmouth; Workshop '\emph{Developments in Macroeconomics}' Univerist\`{a} of Rome La Sapienza; Lacea-Lames, Eafit, Medellin; Spanish Economic Association Simposio, Bilbao.} 
\\
\textbf{2015:} {University of Glasgow, Business School; Mid-West Macro Meeting, University of Washington St. Louis; University of Manchester; Lacea meeting, Santa Cruz, Bolivia; Spanish Economic Association Simposio, Girona.} 
\\
\textbf{2014:} {Rice University, Huston (TX); University of California San Diego; $10^{th}$ Dynare conference, Banque de France, Paris; Lacea Lames meeting, Sao Paulo; Spanish Economic Association Simposio, Palma de Mallorca.} 
\\
\textbf{2013:} {Spanish Economic Association Simposio, Santander; Xi'an Jiaotong-Liverpool University, SuZhou China; 9th Dynare conference, SUFE Shanghai; MBF Workshop, Universita' di Milano Bicocca; Reserve Bank of New Zealand; Universita' di Pavia; Utrecht School of Economics; Universita' di Padova; Workshop on Empirical Macroeconomics, University of Ghent.}
\\
\textbf{2012:} {Spanish Economic Association Simposio, Vigo; Cardiff Business School; SIE, Matera; 8th Dynare Conference, Zurich; CIMS Conference, Guildford; EEA-ESEM University of Malaga; Structural Change and Macroeconomic Dynamics University of Cagliari; University of Porto; Banco de Espa\~{n}a; Workshop on Structural Change \& Macroeconomic Dynamics, University of Cagliari.}
\\
\textbf{2011:} {NIPFP, New Delhi; Structural Change and Macroeconomic Performance workshop at University of 
Cagliari.}
\\
\textbf{2010:} {MONFISPOL Conference, London Metropolitan University, London; Computational Economics and Finance 2010 Conference, Department of Economics,  City University, London; Spanish Economic Association Simposio, Department of Economics,  Universidad Autonoma de Madrid. }
\\
\textbf{2009:} {Spanish Economic Association Simposio, Department of Economics,  University of Valencia; Association of Southern European Economist Annual conference, Department of Economics, Bo\u{g}azi\c{c}i University, Istanbul; 41st Annual Conference, Money Macro and Finance research group, Bradford School of Management, Bradford University; Annual international conference on macroeconomic analysis and international finance, Department of Economics, University of Crete, Rethymno; Department of Financial Economics, University of Hannover; Department of Economics, University of Konstanz.}
\\
\textbf{2008:} {Macroeconomic and Financial Linkages: Theory and Practice. Peterhouse College, University of Cambridge; Association of Southern European Economic Theorists (ASSET) 2008 meeting. EUI, Florence; Doctoral Workshop on Dynamic Macroeconomics, Universite Louis Pasteur Strasbourg; Southern Workshop in Macroeconomics, University of Auckland and Reserve Bank of New Zealand.}
\\
\textbf{2007:} {Second Doctoral Workshop, EBIM, University of Bielefeld.}


\section{\sc{Refereeing Experience}}
\emph{Journal of Political Economy; Quarterly Journal of Economics; The Review of Economic Studies; American Economic Review: Insights; Journal of Monetary Economics; Journal of Economic Theory; Journal of the European Economic Association; The Economic Journal; Review of Economics and Statistics; Review of Economic Dynamics; Journal of Applied Econometrics; International Economic Review; Journal of Economic Dynamics and Control; Journal of Money Credit and Banking; European Economic Review; Macroeconomic Dynamics; Oxford Bulletin of Economics and Statistics; The Scandinavian Journal of Economics; Economic Inquiry; Economic Letters; Oxford Economic papers; BE Journal of Macroeconomics; Journal of Macroeconomics; Economica; SERIEs; Economic Modelling; Southern Economic Journal; Scottish Journal of Political Economy; Bank of England Staff working papers; Deutsche Bundesbank Discussion Paper Series; Czech National Bank Working Papers; ESRC-UKRI; ANVUR (Italian Research Evaluation); PRIN (Italian Minsitry of Education research grants);  Research Grants Council Hong Kong.}


\section{\sc{PhD Supervision and PhD examinations}}
\begin{itemize}
\item PhD Student Supervised: \emph{Vedanta Dhamija (Surrey, 2023)} \emph{Joseph Grilli (Surrey, 2019); Tae Min Lee (Surrey, 2017); Marcelo Almeida (Surrey, 2017); Matteo Ghilardi (Surrey, 2013).}
\item PhD viva committee: \emph{Gregorio Ghetti} (Bicocca, 2025)\emph{Giuliano de Queiroz Ferreira} (S\~ao Paulo, 2023) \emph{Silvio Tunis} (Cagliari, 2023); \emph{Alessandro Cantelmo} (London City, 2018); \emph{Fred Iklaga (Surrey, 2017); Diana Lima (Surrey, 2017); Jonathan Swarbrick (Surrey, 2016); Veronica Arcurio Vasconez (Paris 1, 2015).}
\end{itemize}


\section{\sc{Computer\\ Skills}}
Matlab, Stata, FORTRAN95, Python, Maple, Mathematica, \LaTeX\\

 
\section{\sc{Memberships}}
Royal economic society; American economic association; European economic association; Spanish economic association, Latin American economic association.

\section{\sc{Languages}}
Italian (Native), English (Fluent), Spanish (Fluent).

\section{\sc{Citizenships}}
Italian, British \\



%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------

%
%\section{\sc{References}}
%
%\vspace{.05in}
%\begin{tabular}{@{}p{3in}p{4in}}
%\textbf{Professor Chinhui Juhn}   						& \textbf{Professor Aimee Chin} \\            
%Department of Economics   							& Department of Economics \\         
%University of Houston 								& University of Houston\\       
%Phone: (617) 353-4824 								& Phone: (617) 353-5694\\    
%E-mail:  \href{mailto:cjuhn@uh.edu}{\nolinkurl{cjuhn@uh.edu}}& E-mail:  \href{mailto:achin@uh.edu}{\nolinkurl{achin@uh.edu}}
%\end{tabular}
%
%\vspace{.05in}
%\begin{tabular}{@{}p{3in}p{4in}}
%\textbf{Professor Chinhui Juhn}   						& \textbf{Professor Aimee Chin (Teaching)} \\            
%Department of Economics   							& Department of Economics \\         
%University of Houston 								& University of Houston\\       
%Phone: (617) 353-4824 								& Phone: (617) 353-5694\\    
%E-mail:  \href{mailto:cjuhn@uh.edu}{\nolinkurl{cjuhn@uh.edu}}& E-mail:  \href{mailto:achin@uh.edu}{\nolinkurl{achin@uh.edu}}
%\end{tabular}


%----------------------------------------------------------------------------------------
\centering
updated: June 2025
\end{resume}
\end{document}